Chinese Character Style Transfer with conditional GAN

### 2018-05-03 report/final/egpaper_final.tex
fix typo

\subsection{Font Style Transfer}
A number of previous works have also studied the character style transfer process. "From A to Z" perform style transfer on English characters using variational autoencoder (VAE) \cite{DBLP:journals/corr/UpchurchSB16}. A online project zi2zi\cite{zi2zi} borrows idea from pix2pix, using GAN with encoder-decoder and the U-net structure in the generator to perform font generation in a latent space created by some fixed font styles. Another work AEGN also uses GAN to generate calligraphy using a standard font directly \cite{DBLP:journals/corr/LyuBYZHL17}. A more recent and aligned work is the EMD model, which separate the content and style representation using two distinct encoders \cite{DBLP:journals/corr/abs-1711-06454}.

@@

There are U-Net\cite{DBLP:journals/corr/RonnebergerFB15} like structure which connect the encoder and decoder together with skip-connection to preverse some of the lost information in max-pooling.

@@

For the generator, both binary cross entropy loss and L1 loss is used as suggested by pix2pix. The binary cross entropy loss guides the generator to output images that the discriminator will give high score, i.e. to fool the discriminator. The L1 loss compare the generator's output and the ground truth image.

@@

\begin{enumerate}
	\item Thins stroke might be missing.
	\item The generated image looks "dirty", i.e. has noises.
	\item It failed to learn high level features like spacing between strokes.
\end{enumerate}

@@

31 fonts are obtained onlined. 23 of them are used in style reference training, 5 of them used as context reference and the rest act as test set. 1702 commonly used Chinese characters are picked to be used in training.

>>>>

\subsection{Font Style Transfer}
A number of previous works have also studied the character style transfer process. "From A to Z" perform style transfer on English characters using variational autoencoder (VAE) \cite{DBLP:journals/corr/UpchurchSB16}. A online project zi2zi\cite{zi2zi} borrows idea from pix2pix, using GAN with encoder-decoder and the U-net structure in the generator to perform font generation in a latent space created by some fixed font styles. Another work AEGN also uses GAN to generate calligraphy using a standard font directly \cite{DBLP:journals/corr/LyuBYZHL17}. A more recent and aligned work is the EMD model, which separates the content and style representation using two distinct encoders \cite{DBLP:journals/corr/abs-1711-06454}.

@@

There is U-Net\cite{DBLP:journals/corr/RonnebergerFB15} like structure which connects the encoder and decoder together with skip-connection to preverse some of the lost information in max-pooling.

@@

For the generator, both binary cross entropy loss and L1 loss are used as suggested by pix2pix. The binary cross entropy loss guides the generator to output images that the discriminator will give high score, i.e. to fool the discriminator. The L1 loss compares the generator's output with the ground truth image.

@@

\begin{enumerate}
	\item Thin strokes might be missing.
	\item The generated image looks "dirty", i.e. has noises.
	\item It failed to learn high level features like spacing between strokes.
\end{enumerate}

@@

31 fonts are obtained online. 23 of them are used in style reference training, 5 of them used as context reference and the rest act as test set. 1702 commonly used Chinese characters are picked to be used in training.
